Introduction to *cellcount* - Draft vignette

### 2023-02-27 cellcount_intro.Rmd
Updates to equations and citations

---
title: "Introduction to *cellcount* - Draft vignette"
author: "*T.E. Harman, M. Vandersea, D.E. Berthold, H.D. Laughinghouse, B. Boyd, K. Pokrzywinski*"
date: "12/15/2022"
abstract: >
  The *cellcount* package provides wrapper functions for  [*EBImage*](http://bioconductor.org/packages/devel/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.html) to simplfy quantifying bacteria and cyanobacteria via flourescence microscopy. Cyanobacteria enumeration is an important tool to incorporate data results into mathematical models to assess bloom dynamics. However, standard manual cyanobacteria enumeration is considered time-consuming and can impact overall random error due to different inaccuracies from researcher to researcher. Here, we outline a new open-source tool, *cellcount*, a package designed for the computing language R to assist with cyanobacteria enumeration. Fluorescent microscopy images are analyzed by this package to generate cyanobacteria counts to assess overall cell density from samples.
output: html_document
---

@@

- Total counts (generated previously)
- Height of image field of view (μm)
- Width of image field of view (μm)
- Median cell diameter (μm)
- Total number of images analyzed
- Filtration area (mm^2)
- Volume filtered per image (mL)
- Total sample volume (mL)

Field of view (FOV) is an important variable calculated from image height,
image width, and cell diameter variables. The following equation is listed
below:

$FOV = HW - 2D(H+W)+4D^{2}$

Where:

$H = height$

$W = width$

$D = diameter$

Image height and width are variables that are taken from dimensions 
disseminated by your microscope camera's manufacturer. Please refer to their 
documentation to calculate your FOV variable correctly.

@@

Gregoire, P, Fuchs, F, Sklyar, O, Boutros, M, and Huber, W.
2010. EBImage - an R package for image processing with applications to cellular
phenotypes. Bioinformatics, 26(7), pp. 979-981, 10.1093/bioinformatics/btq046

>>>>

---
title: "Introduction to *cellcount* - Draft vignette"
author: "*T.E. Harman, M. Vandersea, D.E. Berthold, H.D. Laughinghouse, B. Boyd, K. Pokrzywinski*"
date: "02/27/2023"
abstract: >
  The *cellcount* package provides wrapper functions for  [*EBImage*](http://bioconductor.org/packages/devel/bioc/vignettes/EBImage/inst/doc/EBImage-introduction.html) to simplfy quantifying bacteria and cyanobacteria via flourescence microscopy. Cyanobacteria enumeration is an important tool to incorporate data results into mathematical models to assess bloom dynamics. However, standard manual cyanobacteria enumeration is considered time-consuming and can impact overall random error due to different inaccuracies from researcher to researcher. Here, we outline a new open-source tool, *cellcount*, a package designed for the computing language R to assist with cyanobacteria enumeration. Fluorescent microscopy images are analyzed by this package to generate cyanobacteria counts to assess overall cell density from samples.
output: html_document
---

@@

- Total counts (generated previously)
- Height of image field of view (μm)
- Width of image field of view (μm)
- Total number of images analyzed
- Filtration area (mm<sup>2</sup>)
- Volume filtered per image (mL)
- Total sample volume (mL)

Field of view (FOV - mm<sup>2</sup>) is an important variable calculated from image height and
image width. Image height and width are variables that are taken from dimensions 
disseminated by your microscope camera's manufacturer. Please refer to their 
documentation to calculate your FOV variable correctly.

@@

Pau, G, Fuchs, F, Sklyar, O, Boutros, M, Huber, W. 2010. EBImage—an R package for image processing with applications to cellular phenotypes, Bioinformatics, 26(7): 979–981, https://doi.org/10.1093/bioinformatics/btq046
